GVN-Hoist: Hoisting Computations from Branches

### 2016-08-08 hoist.tex
finding the candidates

\subsection{Finding the candidates}
Finding if a set of instructions perform identical computations. Since this code
hoisting is based on GVN, all we need to do is to compare the value number of
computations.

>>>>

\subsection{Finding the candidates}
Finding if a set of instructions perform identical computations. Since this code
hoisting is based on GVN, we need the facility to compute GVN of instructions.
In llvm \cite{llvm}, GVN infrastructure is already set up and works well for
most kind of instructions except loads and store so we compute the GVN of loads
and stores separately. In order to value number stores, we value number (hash)
the address from where the value is to be loaded. For stores, we value number
(hash) the address as well as the value to be stored at that address.

The process of computing GVN can be on-demand (as we come across an instruction)
or, precomputed (computing GVN of all the instructions beforehand). Which
process to choose is determined by the scope of code-hoisting we want to
perform. A pessimistic approach where we want to hoist limited set of
instructions from the sibing branches as we iterate the DFS tree bottom-up, it
is sufficient to compute values on-demand. Whereas, in the optimistic approach,
where we want to hoist as many instructions as possible, would require values to
be precomputed.

Whatever approach we take, to find a candidate all we need to do is to compare
the value number of computations.
